Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-28 1_manuscript/itt-emotion.tex
Add:abstract

  % The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most studies in tourist behavior were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Asian and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the hotel's purely managerial attributes or be more concerned with environmental factors that hotel management cannot change? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

>>>>

  The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most studies in tourist behavior were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the soft attributes a hotel can change or be more concerned with hard attributes that hotel management cannot change? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives. We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
